\section{ARL CONTRIBUTOR LICENSE
AGREEMENT}\label{arl-contributor-license-agreement}

(For use of this form, see ARL Memo 25-88; Form Proponent: RDRL-CII-A)

\subsection{PURPOSE:}\label{purpose}

In order for the United States Government (USG), as represented by the
U.S Army Research Laboratory (ARL), to accept Contributions from
non-Federal Contributors into any projects that it controls, it must
assure itself that any necessary permissions to use certain intellectual
property (IP) rights are granted.

\subsection{PRIVACY ACT NOTIFICATION}\label{privacy-act-notification}

\emph{AUTHORITY}: 10 U.S.C. 3013, Secretary of the Army; 5 U.S.C. 301,
Departmental Regulations, Department of Defense Instruction 5535.8, DoD
Technology Transfer Program and Army Regulation 27-60, Intellectual
Property.

\emph{ROUTINE USES}: In addition to those disclosures generally
permitted under 5 U.S.C 552a(b) of the Privacy Act, these records or
informationcontained therein may specifically be disclosed outside the
DoD as a routine use pursuant to 5 U.S.C 552a(b)(3) as follows: The U.S.
Patentand Trademark Office, Department of Commerce, and/or to the
Copyright Office, Library of Congress. In the event of legal proceedings
andlitigation, information may be disclosed to the Civil Division,
Department of Justice. Parties to a licensing arrangement have access to
thespecific files involved. The `Blanket Routine Uses' set forth at the
beginning of the Army's compilation of systems of records notices
alsoapply to this system.

\emph{DISCLOSURE}: Your disclosure of the requested information is
voluntary. However failure to furnish the requested information will
prevent ARL from considering your contributions.

\subsection{INSTRUCTIONS}\label{instructions}

Fill out each of the fields below as appropriate, and return to ARL via
one of the following methods:

E-mail (Preferred):

usarmy.adelphi.rdecom-arl.list.usarmy-adelphi-md-rdecom-arl-list@mail.mil

Postal Address:

U.S Army Research Laboratory ATTN: RDRL-DPT 2800 Powder Mill Road
Adelphi, MD 20783-1138 USA

If the CLA is signed with pen and is being returned by e-mail, then it
must be scanned so that the USG has a copy of the Contributor's
signature. Contributors that have certificates from a recognized
Certificate Authority may choose to sign their forms electronically, and
e-mail the signed form to ARL. In general, ARL prefers that the CLA be
digitally signed and e-mailed to ARL.

Please read this document carefully before signing, and keep a copy for
your records.

\subsection{AGREEMENT}\label{agreement}

The terms of the following agreement are for Contributions to the
Project:

Project Name: {[}{[}ENTER THE PROJECT NAME HERE{]}{]}

You accept and agree to the following terms and conditions for Your
present and future Contributions to the Project submitted to the USG, as
represented by the U.S. Army Research Laboratory. Except for the license
granted herein to the USG and recipients of software distributed by the
USG, You reserve all right, title, and interest in and to Your
Contributions.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{Definitions}. ``You'' (or ``Your'') shall mean the copyright
  owner or legal entity authorized by the copyright owner that is making
  this Agreement with the USG. For authorized legal entities, the entity
  making a Contribution and all other entities that control, are
  controlled by, or are under common control with that entity are
  considered to be a single Contributor. For the purposes of this
  definition, ``control'' means (i) the power, direct or indirect, to
  cause the direction or management of such entity, whether by contract
  or otherwise, or (ii) ownershipof fifty percent (50\%) or more of the
  outstanding shares, or (iii) beneficial ownership of such entity.
  ``Contribution'' shall mean any original work of authorship, including
  any modifications or additions to an existing work, that is
  intentionally submitted by You to the USG for inclusion in, or
  documentation of, any of the products owned or managed by the USG (the
  ``Work''). For the purposes of this definition, ``submitted'' means
  any form of electronic, verbal, or written communication sent to the
  USG or its representatives, including but not limited to communication
  on electronic mailing lists, source code control systems, and issue
  tracking systems that are managed by, or on behalf of, the USG for the
  purpose of discussing and improving the Work, but excluding
  communication that is conspicuously marked or otherwise designated in
  writing by You as ``Not a Contribution.''
\item
  \textbf{Grant of Copyright License}. Subject to the terms and
  conditions of this Agreement, You hereby grant to the USG and to
  recipients of software distributed by the USG a perpetual, world-wide,
  non-exclusive, paid-up, irrevocable copyright license to reproduce,
  prepare derivative works of, publicly display, publicly perform,
  sublicense, and distribute Your Contributions and such derivative
  works.
\item
  \textbf{Grant of Patent License}. Subject to the terms and conditions
  of this Agreement, You hereby grant to the USG and to recipientsof
  software distributed by the USG a perpetual, worldwide, non-exclusive,
  paid-up, irrevocable (except as stated in this section) patent license
  to make, have made, use, offer to sell, sell, import, and otherwise
  transfer the Work, where such license applies only to those patent
  claims licensable by You that are necessarily infringed by Your
  Contribution(s) alone or by combination of Your Contribution(s) with
  the Work to which such Contribution(s) was submitted. If any entity
  institutes patent litigation against You or anyother entity (including
  a cross-claim or counterclaim in a lawsuit) alleging that Your
  Contribution, or the Work to which you have contributed, constitutes
  direct or contributory patent infringement, then any patent licenses
  granted to that entity under this Agreement for that Contribution or
  Work shall terminate as of the date such litigation is filed.
\item
  You represent that you are legally entitled to grant the above
  licenses. If your employer(s) has rights to intellectual property that
  you create that includes Your Contributions, you represent that you
  have received permission to make Contributions on behalf of that
  employer, that your employer has waived such rights for Your
  Contributions to the USG, or that your employer has executed a
  separate CLA with the USG.
\item
  You represent that each of Your Contributions is Your original
  creation (see section 7 for submissions on behalf of others). You
  represent that Your Contribution submissions include complete details
  of any third-party license or other restriction (including, but not
  limited to, related patents and trademarks) of which you are
  personally aware and which are associated with any part of Your
  Contributions.
\item
  You are not expected to provide support for Your Contributions, except
  to the extent You desire to provide support. You may provide support
  for free, for a fee, or not at all. Unless required by applicable law
  or agreed to in writing, You provide Your Contributions on an ``AS
  IS'' BASIS, WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either
  express or implied, including, without limitation, any warranties or
  conditions of TITLE, NON-INFRINGEMENT, MERCHANTABILITY, or FITNESS FOR
  A PARTICULAR PURPOSE.
\item
  Should You wish to submit work that is not Your original creation, You
  may submit it to the USG separately from any Contribution, identifying
  the complete details of its source and of any license or other
  restriction (including, but not limited to, related patents,
  trademarks, and license agreements) of which you are personally aware,
  and conspicuously marking the work as ``Submitted on behalf of a
  third-party: {[}named here{]}.''
\item
  You agree to notify the USG of any facts or circumstances of which you
  become aware that would make these representations inaccurate in any
  respect.
\item
  You acknowledge that you are providing Your Contribution to the USG on
  a gratuitous basis and that this does not create an obligation on the
  part of the USG of any kind, including, but not limited to:
  remuneration, incorporation of Your Contribution into a Government
  work, or any other obligation.
\item
  You agree that any CLA you submit to the USG may become part of the
  public record should the USG be ordered to release it by a valid court
  order, or other legal means. The USG is not under any obligation to
  inform you of this action before, during, or after it occurs.
\end{enumerate}

\subsection{CONTACT INFORMATION}\label{contact-information}

Full Name: {[}{[}ENTER YOUR FULL NAME HERE{]}{]}

E-mail: {[}{[}ENTER YOUR EMAIL HERE{]}{]}

Postal Address: {[}{[}ENTER YOUR POSTAL ADDRESS HERE{]}{]}

Telephone Number: {[}{[}ENTER YOUR TELEPHONE NUMBER HERE{]}{]}

Fax Number: {[}{[}ENTER YOUR FAX NUMBER HERE{]}{]}

Signature: {[}{[}SIGN HERE{]}{]}
